What is happening on Twitter? A framework for student research projects with tweets

### 2020-09-16 Rmd/reply-to-reviewers.Rmd

> 6)      I really like the rubric.  How closely tied is it to using Twitter data?  What would be different if some other data source were provided?

**Thank you! This is a great point that you make, and, as you seem to suggest, much would not differ with other data sources. We've added text to the manuscript to expand on this point.**

> 7)      I wonder whether the title might be reconsidered.  Perhaps “A framework for student research projects in data science courses”?  The application to Twitter feels secondary to me.

**We appreciate the suggestion. We chose the title with hopes of promoting the use of tweets and text analysis in student research projects. With all of our supplementary materials explicitly dealing with tweets, we feel more comfortable with the current title.**

### 2020-09-16 Rmd/jse-special-issue-2020-october.Rmd
incorporated reviewer comments.

Twitter API use agreements forbid users from sharing complete API query results. 
However, Twitter permits users to share tweet identification numbers. With a tweet 
identification number, a user may query a Twitter API to obtain complete tweet data. In our 
experience, this 
process is incomplete; that is, many tweet identification numbers submitted to the Twitter API return 
no data. Additionally, on repeated querying of the API, different sets of tweet identification numbers
return data. This complicates our goal of making all analyses computationally 
reproducible and motivates our decision to share the tweet IDs of those tweets that 
we actually analyzed (Supplementary files). Should a reader wish to reproduce 
our analysis, we anticipate that she will get complete tweet data
for all or most of these tweet identification numbers from the API. We provide 
R code for this task in the supplementary files.

@@

With future students, we will use a written rubric to evaluate 
theses (Table \@ref(tab:summative)). We'll
share the rubric with our students at the start of the academic year.

>>>>

Twitter API use agreements forbid users from sharing complete API query results. 
However, Twitter permits users to share tweet identification numbers. With a tweet 
identification number, a user may query a Twitter API to obtain complete tweet data. In our 
experience, this 
process is incomplete; that is, many tweet identification numbers submitted to the Twitter API return 
no data. Additionally, some tweet identification numbers return data on the first query, but don't return data on subsequent queries. This complicates our goal of making all analyses computationally 
reproducible and motivates our decision to share the tweet IDs of those tweets that 
we actually analyzed (Supplementary files). Should a reader wish to reproduce 
our analysis, we anticipate that she will get complete tweet data
for all or most of these tweet identification numbers from the API. We provide 
R code for this task in the supplementary files.

@@

With future students, we will use a written rubric to evaluate 
theses (Table \@ref(tab:summative)). We'll
share the rubric with our students at the start of the academic year. With only minor
modifications, the rubric may be suitable for projects that don't use tweets.
